Learning how to act: making good decisions with machine learning

### 2017-04-13 causal-bandit/nips_2016/mem-alloc-poster.tex
long overdue update

\documentclass[nofooter,landscape,scale=1.4]{poster}
\usepackage[absolute,overlay]{textpos}

@@

\title{Causal Bandits: Learning Good Interventions via Causal Inference}
\author{\mbox{}\\[1.3cm] Finnian Lattimore \hspace{2cm} Tor Lattimore \hspace{2cm} Mark Reid}
\footer{Contact}
\date{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock}{25.33}(2,12)
%\setbeamercolor*{block body}{bg=,fg=black}
\begin{block}{Introduction}
\justifying
We study the problem of using causal models to improve the rate at which good interventions can be learned online in a stochastic environment. 
Our formalism combines multi-arm bandits and causal inference to model a novel type of bandit feedback that is not exploited by existing approaches.
We propose a new algorithm that exploits the causal feedback and prove a bound on its simple regret that is strictly better (in all quantities) 
than algorithms that do not use the additional causal information.

\eq{
&\textbf{upper-bound, } R \in \bigo{\sqrt{\frac{m(\vec{q})}{T}\log\left(\frac{NT}{m(\vec{q})}\right)}}\,.\\
&\textbf{lower-bound, }R \in \Omega\left(\sqrt{\frac{m(\vec{q})}{T}}\right)\,.\\
&\textbf{standard lower-bound, }\simpleregret \in \Omega\left(\sqrt{\frac{N}{T}}\right)\,.
}
\end{block}

@@

\vspace{-1cm}
{
%\setbeamercolor*{block body}{bg=white!95!blue,fg=black}
\begin{block}{Optimistic Algorithm}
\begin{algorithmic}[1]
\State {\bf input: } $n, K$, $\set{\ubar \nu_{k,0}}_{k=1}^K$
\State $\delta \leftarrow (nK)^{-2}$ and $\bar \nu_{k,0} = \infty$ for each $k$
\For{$t \in 1, \ldots, n$}
\State /* Optimistically choose $M_{k,t}$ using $\ubar \nu_{k,t-1}$ */
\State $(\forall k \in 1,\ldots,K)$ initialise $M_{k,t} \leftarrow 0$
\For{$i \in 1, \ldots, K$}
\State $k \leftarrow \argmin\limits_{k : M_{k,t} = 0} \ubar \nu_{k,t-1}$
\State $M_{k,t} \leftarrow \min \set{\ubar \nu_{k,t-1},\; 1 - \sum_{j=1}^K M_{j,t}}$
\EndFor
\State $(\forall k \in 1,\ldots,K)$ observe $X_{k,t}$ 
\State $(\forall k \in 1,\ldots,K)$ compute estimates:
\eq{
w_{k,t} &\leftarrow {1 \over 1 - {M_{k,t} \over \bar \nu_{k,t-1}}} 
&{1 \over \hat\nu_{k,t}} &\leftarrow {\sum_{s=1}^{t} w_{k,s} X_{k,s} \over \sum_{s=1}^t w_{k,s} M_{k,s}} 
}
\State $(\forall k \in 1,\ldots,K)$ update confidence intervals:
\eq{
R_{k,t} &\leftarrow \max_{s \leq t} w_{k,s}  \qquad \hat V^2_{k,t} \leftarrow \sum_{s \leq t} {w_{k,s} M_{k,s} \over \ubar \nu_{k,t-1}} \\
\tilde \epsilon_{k,t} &\leftarrow {f(R_{k,t}, \hat V^2_{k,t},\delta) \over \sum_{s=1}^t w_{k,s} M_{k,s}}    \\
{1 \over \ubar \nu_{k,t}} &\leftarrow \min\set{{1 \over \ubar \nu_{k,t-1}}, {1 \over \hat \nu_{k,t}} + \tilde\epsilon_{k,t}} \\
{1 \over \bar \nu_{k,t}} &\leftarrow \max\set{{1 \over \bar \nu_{k,t-1}}, {1 \over \hat \nu_{k,t}} - \tilde\epsilon_{k,t}} 
}
\EndFor
\Statex 
\Function{$f$}{$R$,$V^2$, $\delta$}
\State $\delta_0 \leftarrow {\delta \over 3(R+1)^2 (V^2+1)^2}$
\State \Return 
${R+1 \over 3} \log{2 \over \delta_0}$
\Statex $\qquad +\;\;\sqrt{2(V^2+1) \log{2 \over \delta_0} + \left({R+1 \over 3}\right)^2 \log^2{2 \over \delta_0}}$
\EndFunction
\end{algorithmic}
\end{block}
}

>>>>

\documentclass[nofooter,scale=1.4]{poster}
\usepackage[absolute,overlay]{textpos}

@@

\title{Optimal Resource Allocation with Semi-Bandit Feedback}
\author{\mbox{}\\[1.3cm] Tor Lattimore \hspace{2cm} Koby Crammer \hspace{2cm} Csaba Szepesv\'ari}
\footer{Contact}
\date{}

@@

\begin{textblock}{20}(0,5)
\includegraphics[height=8cm]{UoA-logo}
\end{textblock}

\begin{textblock}{20}(68,7)
\includegraphics[height=5cm]{technion-logo}
\end{textblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{textblock}{25.33}(2,12)
%\setbeamercolor*{block body}{bg=,fg=black}
\begin{block}{Introduction}
\justifying
We study a sequential resource allocation problem involving a fixed number of recurring jobs.
%
At each time step the learner should distribute available resources among the jobs in order to maximise the expected number of completed jobs. 
%
Allocating more resources to a given job increases the probability
that it completes, but with a cut-off. %KC diminishing returns. 
Specifically, we assume a linear
model where the probability increases linearly until it equals one, after which
allocating additional resources is wasteful.
%
We assume the difficulty of each job is unknown
and present the first algorithm for this problem and prove upper and lower bounds on its regret.
Despite its apparent simplicity, the problem has a rich structure: 
We show that an appropriate optimistic algorithm can improve its learning speed dramatically 
beyond the results one normally expects for similar problems
as the problem becomes resource-laden.
\end{block}

@@

\vspace{-1cm}
{
\setbeamercolor*{block body}{bg=white!95!blue,fg=black}
\begin{block}{Optimistic Algorithm}
\begin{algorithmic}[1]
\State {\bf input: } $n, K$, $\set{\ubar \nu_{k,0}}_{k=1}^K$
\State $\delta \leftarrow (nK)^{-2}$ and $\bar \nu_{k,0} = \infty$ for each $k$
\For{$t \in 1, \ldots, n$}
\State /* Optimistically choose $M_{k,t}$ using $\ubar \nu_{k,t-1}$ */
\State $(\forall k \in 1,\ldots,K)$ initialise $M_{k,t} \leftarrow 0$
\For{$i \in 1, \ldots, K$}
\State $k \leftarrow \argmin\limits_{k : M_{k,t} = 0} \ubar \nu_{k,t-1}$
\State $M_{k,t} \leftarrow \min \set{\ubar \nu_{k,t-1},\; 1 - \sum_{j=1}^K M_{j,t}}$
\EndFor
\State $(\forall k \in 1,\ldots,K)$ observe $X_{k,t}$ 
\State $(\forall k \in 1,\ldots,K)$ compute estimates:
\eq{
w_{k,t} &\leftarrow {1 \over 1 - {M_{k,t} \over \bar \nu_{k,t-1}}} 
&{1 \over \hat\nu_{k,t}} &\leftarrow {\sum_{s=1}^{t} w_{k,s} X_{k,s} \over \sum_{s=1}^t w_{k,s} M_{k,s}} 
}
\State $(\forall k \in 1,\ldots,K)$ update confidence intervals:
\eq{
R_{k,t} &\leftarrow \max_{s \leq t} w_{k,s}  \qquad \hat V^2_{k,t} \leftarrow \sum_{s \leq t} {w_{k,s} M_{k,s} \over \ubar \nu_{k,t-1}} \\
\tilde \epsilon_{k,t} &\leftarrow {f(R_{k,t}, \hat V^2_{k,t},\delta) \over \sum_{s=1}^t w_{k,s} M_{k,s}}    \\
{1 \over \ubar \nu_{k,t}} &\leftarrow \min\set{{1 \over \ubar \nu_{k,t-1}}, {1 \over \hat \nu_{k,t}} + \tilde\epsilon_{k,t}} \\
{1 \over \bar \nu_{k,t}} &\leftarrow \max\set{{1 \over \bar \nu_{k,t-1}}, {1 \over \hat \nu_{k,t}} - \tilde\epsilon_{k,t}} 
}
\EndFor
\Statex 
\Function{$f$}{$R$,$V^2$, $\delta$}
\State $\delta_0 \leftarrow {\delta \over 3(R+1)^2 (V^2+1)^2}$
\State \Return 
${R+1 \over 3} \log{2 \over \delta_0}$
\Statex $\qquad +\;\;\sqrt{2(V^2+1) \log{2 \over \delta_0} + \left({R+1 \over 3}\right)^2 \log^2{2 \over \delta_0}}$
\EndFunction
\end{algorithmic}
\end{block}
}

### 2017-04-13 causal-bandit/nips_2016/poster/causal_bandits_poster.tex
long overdue update

\documentclass[b0,landscape,25pt]{sciposter}

@@

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit
\begin{minipage}[t]{0.15\linewidth}%
\centering
\includegraphics[height=12cm]{nicta_logo2.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}
\begin{minipage}[b]{0.65\linewidth}
\centering
\resizebox{\linewidth}{!}{\veryHuge \color{NavyBlue} \textbf{Causal Inference in Machine Learning: A review}}
 \color{Black}\\

\huge \textbf{Finnian Lattimore}\\ % Author(s)
\huge Australian National University\\ % University/organization
finnlattimore@gmail.com

\end{minipage}
\begin{minipage}[t]{0.15\linewidth}
\centering
\includegraphics[height=12cm]{anu-logo-notext}
\end{minipage}

>>>>

\documentclass[a0,landscape,25pt,plainsections]{sciposter}

@@

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit
%\begin{minipage}[t]{0.15\linewidth}%
%\centering
%%\includegraphics[height=12cm]{nicta_logo2.jpg} % Logo or a photo of you, adjust its dimensions here
%\end{minipage}
\begin{minipage}[b]{0.99\linewidth}
\centering
\resizebox{\linewidth}{!}{\veryHuge \color{NavyBlue} \textbf{Causal Bandits: Learning Good Interventions via Causal Inference}}
 \color{Black}\\

\huge Finnian Lattimore, Tor Lattimore and Mark Reid\\ % Author(s)

\end{minipage}
%\begin{minipage}[t]{0.15\linewidth}
%\centering
%%\includegraphics[height=12cm]{anu-logo-notext}
%\end{minipage}

### 2017-04-13 thesis/thesis_map.tex
long overdue update

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage[noend]{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{parskip}
\usepackage{tikz}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usetikzlibrary{arrows,positioning} 
\usepackage{subcaption}

@@

\section*{Notes on papers}
from association to causation via regression (Freedman)
very clear description of the goal of causal inference, very critical causal modelling due to the impossibility of empirically assessing the assumptions.

\section*{What is causality and why do we care?}

The meaning of causality remains widely debated within science and philosophy ...

For this thesis I define a causal model to be any model that aims to predict the outcome of an action or intervention in some system. From this viewpoint, most real problems require causal inference. What use is a model if you are not going to use it to guide any decisions? How then can machine learning be integrating itself into so many key aspects of our lives, while causal inferene remains a small subfield mostly of interest to economists? The answer is two-fold. For some problems, the effect of a decision is obvious and does not impact the system on which it was based. In these cases, the causal aspect of the problem can be safely ignored. Secondly it is likely that machine learners and data scientits, bouyed by successes in the former problems and the excitement of a world awash with data, computing power and non-linear models are overlooking the fact that their predictions may no longer hold if people act on them. Consider the following problems, do they require causal inference?

notes: We don't always need to predict the outcome of an action. In somes

The goal may be more limitied than predicting the outcome of an intervention. To decide between actions, we only assumptions or estimates as to which is better.

For example, in the speech recognition, the immediate result of the action may be known and deterministic (Siri does something). The full consequences of that action are not modelled, (we assume the desired outcome is that Siri )

\begin{itemize}
\item Speech recognition (for systems like Siri or Google)
\item Machine translation 
\item Image classification
\item Forecasting the weather
\item Playing Go 
\item Identiying spam emails
\item Automated essay marking
\item Predicting the risk of death in patients with pnumonia.
\item Predicting who will re-offend on release from prison 
\item Predicting which customers will cease to be your customers
\item Demand prediction for inventory control
\item Predicting who will click on an ad

\item Financial trading
\item Recommending movies
\item Online search
\item Self driving cars

@@

The above problems are not posed with enough detail to know if causality is an important consideration. In particular, I failed to specify what actions the might be taken in response to model.

Consider speech recognition. You say something, which causes to sound waves, which are converted to a digital signal which Siri maps to words. Whatever action Siri takes is unlikely to change the distribution of words you use, and even less likely to change the function that maps sound waves to text (unless she sends you a dvd on elocution). A similar arguament could be made for many applications of machine translation and image classification. What about forecasting the weather? If you are using a short term forecast to decide whether to pack an umbrella it's clear causality can be ignored - your decicion will not effect if it actually rains. However, longer term climate forecasts might (theoretically) lead us to take action on emissions which would then change the weather system. For this we need a (causal) model that allows us to predict the outcome under various different interventions.

Identifing spam and automated essay marking systems are similar. The decision made by the algorithm is likely to change the relationship between the features used by the algorithm and the true label. Spammers and students will modify their writing in order to optimise thier results. These systems can only work if the resulting change is sufficiently gradual and fresh ground truth (probably human labelled) training data is provided. (What would the nature of the features have to be such that change did not occur? - they would have to be causes of the label.

What about predicting the risk of death in patients with pnumonia? Suppose we wish to use the model to decide who should be treated in hospital and who can be sent home with antibiotics. If we assume that in hospital treatment is more effective this seems like a straighforward prediction problem. It is not. Depending on how the decision to admit was previously made and what features are included (or ommited) in the model, the relationship between those features and the outcome may change if we start using the model to decide whome to admit. (xxx et al) found exactly this effect. Their model learnt that (among other things) people suffering asthma were LESS likely to die from pnemonia. They realised this was because doctors were treating such patints very agressively, thus acutally lowering their risk. There is no problem with this model if you want to predict who would be likely to die whilst maintaining the original admition and treatment protocols. However, using it to decide who to admit could kill. The key is understanding exactly what question you are asking. In this case we are care about what happens to patients with characteristics X if we treat them according to decision rule Z.

Predicting which customers will leave or who will re-offend if granted parole also fit within the category of problems where you wish to identify a group for which a problem will occur and target some treatment to them (loyalty reward, deny parole or more support whilst on parole, etc). For all these problems the assumptions required to treat them as pure prediction problems are;
\begin{enumerate}
\item The treatment is assumed to be effective (at least better than nothing)
\item Deciding who to treat on the based of the model predictions won't change the relationship between features and outcome 
\end{enumerate}
It is easy to see how similar issues to the pneumonia example could occur for the customer and parole cases. For example, if the customer retention model is not aware of existing customer loyalty schemes or the most risky criminals are currently only given parole in exceptional circumstances (not visable to the model) so rarely offend. If people are aware of the model they may also try to game it (as in the spam/essay example) so as to recive loyalty reward or early release. TODO talk about the interesting long-term vs short term dilema introduced by the parole example. (maybe best to discuss it further on)

Demand prediction seems relatively straightforward. These models use features such as location, pricing, marketing, time of year, weather, etc to forecast the demand for a product. It seems unlikely that using the model to ensure stock is available will itself change demand. However there is a potential data sensoring issue. If demand is modelled by the number of sales, then if a product is out of stock demand will appear to be zero. Changing availability does then change demand.

Playing Go (and other games) is another case with some subleties. At every turn, the AI agent has a number of actions available. The board state following each action is deterministic and given by the rules of the game. The agent can apply supervised machine learning based on millions of previous games to estimate the probability that each of these board states will lead to a win. ... this is interesting maybe come back to it ... an alternate approach would be to try to forecast the probability of a win given each action given the current board state as context ... One approach to causal inference is indeed to learn about actions from taking actions (or observing the actions that other have taken). When can we learn from the actions others have taken? When there is no confounding. And does this hold with Go? Probably because the board state encapsulates everything that should determine what move is played. Learning directly from actions and trying to generalize (can in some instances reduce the problem to standard ML)

I hope these examples gave you a feel for the richness and subtlties of causal inference. We will return to some of them in more detail once we have established some more concrete language and tools to approach them with.

I do not see the distinction between explaination and (causal) prediction. Explaination is all about the ability to compress and to generalize. The more a model can do this, the more we view as providing an understanding of the why.

Does this definition include mediation?

Sometimes the causal component is obvious.

Relationship to generalization. Variables causally directly causally related to the outcome (either causes or effects) should be more stable predictors over time. The assumption is there are less places for change to come in.

If a feature is a cause of an outcome then changing the input distribution over that feature won't break the model. If its an effect it could.

The direct causes (and effects) of a variable of interest make up a sufficient set for prediction (is this true)? This may be a reason for using structure learning type algorithms even if you are simply doing prediction.

\subsubsection*{The role of assumptions in causal inference}

Fundamental challenges. How do you cross-validate or compare causal inference models? Lack of real world data on which to compare algorithms.

Does predictive accuracy indicate a good causal model?

Assumptions must be recognised. Without assumptions - only description is possible. Recognising the assumption (and associated risk) means that we understand we should still attempt to experiment.

Generalizing the results of one experiment to another (for example, dropping rocks to dropping people - with reference to the cross over trial for parashutes.) (This I think is the long term key to successful causal inference, learning from experimental data with representations that generalize). (and given sufficient generalizability, it may not matter if there is an underlying confounder - as this confounder is clearly not changing much)

Is causal inference possible (are the conclusions ever valid)?

Only from randomized experiment ... if people can do it without recource to constant randomized experiment then an algorithm exits.

The challenges and limitations of infering causal effects from observation data are numerous. However, there are problems we need to solve. The questions is are these problems so serious as to warrent discregarding all non-experimental data. I think answer is a clear no. Need ongoing validation, with assumptions. We can't validate the assumptions using the observational data alone (otherwise we would not have been forced to make them).

\subsection*{Mediation}
\subsection*{Relationship to interpretability}

@@

Are causal/interpretable models more reliable or more likely to generalize well?

@@

If we know the training and test data will be sampled from different distributions, knowing what the features that the model is looking at are, allows people use their background understanding of the world to evaluate whether or not those features are likely to be transferable to the test domain.

@@

People have access to a lot of detailed prior knowledge.

\subsection*{Relationship to transfer learning}

find a feature representation in which $P(Y|X)$ is the same in many different domains (or stable over time). Causal models predict the outcome of actions. We could directly take these actions and learn $P(Y|a,X)$ for every $(a,X)$ but, in reality, no two situations (or actions) are exactly alike. So we have to make representations such that things are stable.

@@

For example, in the advertising setting, we want to know how our on expenditure on paid search ads is linked to sales. However, this relationship may be very unstable over time because the ad slots are sold at auction. The amount we have to pay to obtain a given position for keyword depends crucially on the amount our competitors are bidding for that keyword. However, the relationship between displaying the ad at a particular position and the probability that someone clicks it an then makes a purchase may be much more consistent.

\subsection*{The two approaches to causality}

What are the issues with standard randomized experiments?

\section*{Causal Inference}

\subsection*{Models of causality and intervention}
\subsubsection*{DAGs}

Although seemingly simplistic, the notion of hard interventions is surprisingly powerful.

\subsubsection*{Counterfactuals}

@@

A translator from graphical independence to counter factual statements.

@@

\section*{Multi-armed Bandits}

\section*{Unifying the frameworks}
\label{sec:unificaition}

@@

\section*{Data for testing causal models}
Simulators. Open competitions. Converting other data sets. Existing data sets.

>>>>

\documentclass[11pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage[noend]{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{parskip}
\usepackage{tikz}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usetikzlibrary{arrows,positioning} 
\usepackage{subcaption}

@@

\section{This Thesis}
\begin{itemize}
\item clarify where causal inference fits within machine learing, for which problems it is required and ...
\end{itemize}

\section*{Uncategorized}
http://www.news.com.au/finance/money/costs/insurance-companies-secrets-spilt/news-story/f6ef17ae73e3a5636343845666532b91 insurance decisions voodoo because of lack of transparancy and absense of obvious causal link. Claim: People are more comfortable with desicion making on the basis of factors they believe to be causally relevet.

\chapter*{Introduction (3500 words)}

\paragraph*{Motivating summary}

\section*{What is causality and why do we care? (2000 words)}

\subsection*{Defining causality}
\begin{itemize}
\item widely debated in science and philosophy (FIND SOME REFERENCES)
\item what is explaination?
\item any model that aims to predict the outcome of an action or intervention in a system
\item I do not see the distinction between explaination and (causal) prediction. Explaination is all about the ability to compress and to generalize. The more a model can do this, the more we view as providing an understanding of the why. 
\item mediation?
\end{itemize}

\subsection*{Identifying when we have a causal problem}

\subsubsection*{Examples of typical machine learning probems. Are they causal?}

\begin{itemize}
\item Speech recognition (for systems like Siri or Google)
\item Machine translation 
\item Image classification
\item Forecasting the weather
\item Playing Go 
\item Identiying spam emails
\item Automated essay marking
\item Predicting the risk of death in patients with pnumonia.
\item Predicting who will re-offend on release from prison 
\item Predicting which customers will cease to be your customers
\item Demand prediction for inventory control
\item Predicting who will click on an ad
\item Financial trading
\item Recommending movies
\item Online search
\item Self driving cars
\end{itemize}

\subsubsection*{What aspects of a problem determine if causal inference is required?}
(When is pure prediction useful?)
\begin{itemize}
\item To decide between actions we only need to rank them (not estimate their actual effect). 
\item The predicted outcome in the absence of an intervention provides a single point. We can use this to find which problems are most serious if left alone - and priortise those for modelling changes. 
\item Any decision we take does not significanly impact the system from which the data was drawn to make it (for repeat decision making)
\item Does acting on the result of the prediction change the predictive distribution p(y|x)? Ie change people's behaviour.

@@

\section*{Approaches to causality (1000 words)}

\paragraph*{Two broad approaches} 
\begin{itemize}
\item Build a model to map the natural behaviour of the system to what will happen for some action
\item Take the action and see what happens
\end{itemize}

\paragraph*{The first is causal inference}

\paragraph*{The second is reinforcement learning}

\paragraph*{Both generalize from randomized experiment} Reinforcment learning to sequential decisions, causal inference to non-experimental conditions

\paragraph*{Both approaches involve assumptions} the latter that we can group context and actions.

\paragraph*{Limitations of causal inference}

\paragraph*{Limitations of experimets} What are the issues with standard randomized experiments?

\chapter*{Causal models (5000 words)}
\subsection*{Causal graphical models}
Although seemingly simplistic, the notion of hard interventions is surprisingly powerful.

\subsection*{Counterfactuals}
\subsection*{Structural Equation models}
\subsection*{Comparing and unifying the models}
\subsubsection{A translator from graphical independence to counter factual statements}

\chapter*{Two key questions (5000 words)}
\section*{Causal Inference} 
\paragraph*{You are willing to assume the causal graph}
\paragraph*{extremely widely appliled} Implicitly accounts 10,000 of studies in phycology, medicine, business, etc.

\subsection*{Identifiability}
\paragraph*{Under what conditions in is the problem solveable}
\subsubsection*{The Do Calculus}

\subsubsection*{Open questions within identifiablity}

\subsection*{Estimation}
\paragraph*{How well do we actually do with finite datasets?}

\section*{Causal Discovery}
\paragraph*{You want to learn the graph}
\paragraph*{Equates to the aim of automating scientific discovery}
\paragraph*{Increadibly hard}
\subsection*{Discovery with Conditional independence}
\subsection*{Discovery with Functional Models}

\chapter*{Multi-Armed Bandits (5000 words)}

\chapter*{Causal Bandits: Unifying the approaches (5000 words)}

\chapter*{Causal Inference \& Machine Learning (5000 words)}
A more detailed discussion on where causal inference sits within machine learning and what it can offer.

\section*{Different approaches}
\paragraph{The two cultures}

\subsubsection*{Translating terminology}
Economist -> ML

\section*{Challenges for the Machine learning approach}
\subsection*{No cross validation}
\paragraph*{The challenge of model selection}
\paragraph*{Does predictive accuracy indicate a good causal model?}
\subsection*{Less large, real world datasets}
\paragraph*{The dearth of experimental data}
\subsubsection*{Data for testing causal models}
Simulators. Open competitions. Converting other data sets. Existing data sets.

\section*{Relation to other areas of ML}
\subsection*{Covariate shift}
\subsection*{Generalizability}
\paragraph*{Invariants}
\paragraph{more stable} Variables causally directly causally related to the outcome (either causes or effects) should be more stable predictors over time. The assumption is there are less places for change to come in.

\paragraph{change input distribution}If a feature is a cause of an outcome then changing the input distribution over that feature won't break the model. If its an effect it could.

\paragraph{feature selection} The direct causes (and effects) of a variable of interest make up a sufficient set for prediction (is this true)? This may be a reason for using structure learning type algorithms even if you are simply doing prediction.
\subsection*{Interpretabilty}
\paragraph*{interpretable models as proxies for causal models} Let the human do the work. If we know the training and test data will be sampled from different distributions, knowing what the features that the model is looking at are, allows people use their background understanding of the world to evaluate whether or not those features are likely to be transferable to the test domain.

@@

@@

@@

People have access to a lot of detailed prior knowledge.  
\subsection*{Transfer Learning}
find a feature representation in which $P(Y|X)$ is the same in many different domains (or stable over time). Causal models predict the outcome of actions. We could directly take these actions and learn $P(Y|a,X)$ for every $(a,X)$ but, in reality, no two situations (or actions) are exactly alike. So we have to make representations such that things are stable.

@@

For example, in the advertising setting, we want to know how our on expenditure on paid search ads is linked to sales. However, this relationship may be very unstable over time because the ad slots are sold at auction. The amount we have to pay to obtain a given position for keyword depends crucially on the amount our competitors are bidding for that keyword. However, the relationship between displaying the ad at a particular position and the probability that someone clicks it an then makes a purchase may be much more consistent. 
\subsection*{Fair Machine Learning}

@@

@@

\chapter*{Conclusions (1000 words)}

@@
